paper

### 2022-03-30 outputs/paper.Rmd
Map of Ghana Distribution of the number of women employed in different regions

```{r readdata, echo=FALSE}
ghana<-read_csv('data/cleaned_data.csv', show_col_types = FALSE)
```

@@

```{r total, echo=FALSE, fig.cap="Data"}
ghana %>%
  mutate(
    character = factor(character,
                       levels=c("Residence",
                                "Region",
                                "Mother\'s_education",
                                "Work_status",
                                "Occupation",
                                "Employment_status",
                                "Total"
                                )
                       )
           ) %>%
  group_by(character) %>%
  summarise(sum = sum(number_of_employed_women))
```

@@

>>>>

```{r readdata, echo=FALSE}
ghana <- read_csv('data/cleaned_data.csv', show_col_types = FALSE)
```

@@

```{r total, echo=FALSE, fig.cap="Data"}
ghana %>%
  mutate(
    character = factor(character,
                       levels = c("Residence",
                                "Region",
                                "Mother\'s_education",
                                "Work_status",
                                "Occupation",
                                "Employment_status",
                                "Total"
                                )
                       )
           ) %>%
  group_by(character) %>%
  summarise(sum = sum(number_of_employed_women))
```

@@

```{r map, warning = FALSE, echo = FALSE}
library(rnaturalearth)
library(sf)
#devtools::install_github("ropensci/rnaturalearthhires")
# The st_centroid function takes the sf object and returns the center of 
# the polygon, again as a sf object.
map_ghana <- ne_states(country = 'Ghana', 
                       returnclass = 'sf')  # grab provinces within Ghana

map_ghana %>% 
  ggplot() +
  geom_sf( ) + 
  geom_text(data = st_centroid(map_ghana), 
            size = 3,
             aes(x = longitude, 
                 y = latitude,
                 label= woe_name)) +
  labs(title='Ghana Administrative Regions') +
  theme_minimal()
```

```{r, echo=FALSE}
# Urban vs Rural

# Obtain subset of dataset for residence area
residence <- ghana %>% 
  filter(character == 'Residence')

# look at survey respondents distribution in urban and rural areas
residence %>% 
  ggplot(aes(x = background, y = number_of_employed_women)) +
  geom_bar(stat = 'identity', fill = "burlywood") +
  labs(x = "Area",
       y = "Number of employed women") +
  theme_minimal()
```

```{r, echo=FALSE}
# region subdataset
region <- ghana %>% 
  filter(character == "Region") %>% 
  mutate(background = recode(background,
                             'Western' = 'Western',
                             'Central' = 'Central',
                             'Greater_Accra' = 'Greater Accra',
                             'Volta' = 'Volta',
                             'Eastern' = 'Eastern',
                             'Ashanti' = 'Ashanti',
                             'Brong_Ahafo' = 'Brong Ahafo',
                             'Northen' = 'Northern',
                             'Upper_West' = 'Upper West',
                             'Upper_East' = 'Upper East'))

# number of survey respondents in the different administrative regions
region %>% 
  ggplot(aes(x = background,
             y = number_of_employed_women)) +
  geom_bar(stat = 'identity',
           fill = 'burlywood') +
  labs(x = "Administrative regions",
       y = "Number of employed women") +
  theme_minimal()
```

```{r}

```
